---
title: "R Notebook"
output: html_notebook
---

# Import Incidents
```{r}
library(vairkkoexport)

incidents_path <- here::here("data/incidents_export.rds")

if (fs::file_exists(incidents_path)) {
  incidents <- read_rds(incidents_path)
} else {
  incidents <- export_behavioral_incidents()
  write_rds(incidents, here::here("data/incidents_export.rds"))
}

# save length?
incidents %>% mutate(detail_narrative = str_trim(detail_narrative),
                     detail_visibility = str_trim(detail_visibility)) -> incidents


#save incidents:
incidents %>% head()
```



# Wrangle into acceptable format
Next, we're going to work on encapsulating incident as a standardized format.

- Username
- EmployeeID
- SSN
- Employee External Id
- EIN Tax Id
- EIN Name
- Incident Type: 50 char, standardized
- Incident Name: 100 char
- Internal Name: 100 char (incident ID)
- Violation: 50 char, standardized
- Incident Date: mm/dd/YYYY
- Incident Time: HH:MM
- Report Date: mm/dd/YYYY
- Start Date: HH:MM (report time)
- Status: c("Opened", "Initiated", "In Progress", "Closed")
- Priority: c("","Low", "Medium", "High")
- Description: 1024 char
- Employee Signed Date: mm/dd/YYYY
- Reviewer Name
- Reviewer EIN Tax Id
- Reviewer Signed Date: mm/dd/YYYY
- Closed Date: mm/dd/YYYY
- Target Date: mm/dd/YYYY
- Resolved Date: mm/dd/YYYY
- Resolution: 50 char, standardized
- Details: 1024 char (resolution details)

What does raw data look like?
```{r}
head(incidents)
```

Let's start by building out the easy output pieces:
```{r}
incidents %>% mutate(out.incident_date = detail_incident_date,
                     out.username = Member,
                     out.reviewer_name = `Created By`,
                     out.target_date = Updated,
                     out.internal_name = IncidentID) -> incidents
```


Next, evaluate title length.
```{r}
incidents %>% filter(str_length(incidents$Title)>100) %>% pull(Title)
```
Can we trunc this?
```{r}
incidents %>% filter(str_length(incidents$Title)>100) %>% mutate(Title = str_trunc(Title, 100)) %>%  pull(Title)
```
```{r}
incidents %>% mutate(out.incident_name = str_trunc(Title, 100)) -> incidents
```

## Build Action type -> Incident Type Resolution
Next, we need to get incident resolution from the action type field. A bug in the export function yielded a number of "action Type" values that were incorrect. However, it's included in every action text, so we extract from there.

This feeds into the action type crosswalk.

```{r}
incidents %>% count(action_type) %>% arrange(desc(n))  %>% clipr::write_clip() %>% print()
```
Build out crosswalk and attach.
```{r}
action_types_crosswalk <- read_csv(here::here("data/Action_Types_crosswalk.csv")) %>% mutate(action_type = `Action Type`)

incidents %>% left_join(action_types_crosswalk) -> incidents

incidents %>% mutate(out.resolution = `Incident Type Resolution`) -> incidents
incidents %>% count(out.resolution)
```

## Check status fields
```{r}
incidents %>% count(Status, detail_status)
```
Save status
```{r}
incidents %>% mutate(out.status = case_when(Status == "Closed" ~ "Closed",
                                            Category == "" ~ "Initiated",
                                            Actions == 0 ~ "Opened",
                                            TRUE ~ "In Progress")) -> incidents
```


## Build Violation -> Categories
Evaluate Categories (this then feeds into Category -> Violation Type Crosswalk later)
```{r}
incidents %>% count(Category) %>% arrange(desc(n)) %>% clipr::write_clip() %>% print()
```
### Are there missing action types?
```{r}
incidents %>% filter(Actions > 0, is.na(action_type)) %>% View()
```



### Fix the missing categories
How many incidents missing a category?
```{r}
incidents %>% filter(Category == "") %>% tally()
```
Fix this.
```{r}
incidents %>% filter(Category == "", 
                     !str_detect(str_to_lower(Title), "kudos|kuddo|came in for co-worker|great"),
                     !str_detect(str_to_lower(Title), "safety|fleet|99b|backing"),
                     !str_detect(str_to_lower(Title), "damag"),
                     !str_detect(str_to_lower(Title), "call off|tardy|left shift|attendance|late|no show|left work early"),
                     !action_type %in% c("Demotion","Termination","Oral","Suspension","Written","Verbal Warning"),
                     !str_detect(str_to_lower(Title), "test|disregard"),
                     !str_detect(str_to_lower(Title), "controlled medication|narcotics")
                     ) %>% View()

incidents %>% mutate(adj_category = case_when(str_length(Category) > 0 ~ "",
                                              str_detect(str_to_lower(Title), "kudos|kuddo|came in for co-worker|great") ~ "Praise",
                                              str_detect(str_to_lower(Title), "safety|99b") ~ "Safety Violation",
                                              str_detect(str_to_lower(Title), "fleet|backing") ~ "Vehicle Operations Violation",
                                              str_detect(str_to_lower(Title), "damag") ~ "Gross Misconduct",
                                              str_detect(str_to_lower(Title), "call off|tardy|left shift|attendance|late|no show|left work early") ~ "Attendance/Tardiness",
                                              str_detect(str_to_lower(Title), "test|disregard") ~ "test",
                                              action_type %in% c("Demotion","Termination","Oral","Suspension","Written","Verbal Warning") ~ "Policy Violation",
                                              str_detect(str_to_lower(Title), "controlled medication|narcotics") ~ "Controlled Medication Policy Violation",
                                              Category == "" ~ "Policy Violation")) -> incidents
incidents %>% count(adj_category)
```



Now, build the violations crosswalk on the outside and join.
```{r}
violations_crosswalk <- read_csv(here::here("data/violations_crosswalk.csv"))

incidents %>% left_join(violations_crosswalk) -> incidents

incidents %>% unite(col="Violation", Violation, adj_category, na.rm=TRUE, sep="") -> incidents

incidents %>% count(Violation)
incidents %>% mutate(out.violation = Violation) -> incidents
```

## Build out closed and signed dates
```{r}
incidents %>% mutate(out.priority = "",
                     out.signed_date = str_extract(action_read_acknowledged, "(?<=First Seen\\n)\\d+/\\d+/\\d+"),
                     out.closed_date = if_else(Status == "Open", "", action_date)
                     ) -> incidents
```

## Build narratives

Create a composite narrative text
```{r}

join_detail <- function(condition, text, noun_sg, noun_pl) {
  case_when(condition > 1 ~ paste0("This incident has ", condition, " ", noun_pl, ".",
                                   "\n", text, "\n",
                                   strrep('-', 60)),
            condition == 1 ~ paste0("This incident has ", condition, " ", noun_pl, ".",
                                    "\n", text,"\n",
                                    strrep('-', 60)),
            condition == 0 ~ paste0("This incident has ", condition, " ", noun_sg, ".")
           )
}

incidents %>%  
  replace_na(list(Actions = 0,
                  Appeals = 0,
                  Comments = 0,
                  Files = 0,
                  Points = 0)) %>% 
  mutate(composite_action = glue::glue("ACTION DETAILS: {action_type}
                                       {if_else(is.na(action_created),'Action by ',paste0(action_created, ' by '))}{action_author}
                                       {str_trim(action_text)}
                                       Action Files: {if_else(action_files == '', 'None', str_trim(action_files))}
                                       Action read/acknowledged? {action_read_acknowledged} 
                                       ")) -> incidents

  incidents %>%  
    mutate(previous_incident = if_else(str_length(detail_previous_incident)>0,
                                       paste0('\nRelated to prior incident ', detail_previous_incident),
                                       "\nNo related incidents")) %>% 
  mutate(composite_narrative = glue::glue("{detail_narrative}
                                          -------------------------------------------------------------
                                          {join_detail(Actions, composite_action, 'action', 'actions')}
                                          {join_detail(Appeals, detail_appeals, 'appeal', 'appeals')}
                                          {join_detail(Comments, detail_comments, 'comment', 'comments')}
                                          Files: {Files}{previous_incident}
                                          
                                          []
                                          ")) -> incidents

max(str_length(incidents$composite_narrative))
```

```{r}
incidents %>% ggplot(aes(str_length(composite_narrative))) + geom_histogram() + geom_vline(xintercept=1024) + scale_x_log10()
```
We'll truncate, but add appendix test:
```{r}
1024-str_length("...\nSee archived detail for full text.")
```
```{r}
incidents %>% 
  mutate(out.description = paste0(str_trunc(composite_narrative, 986), "\nSee archived detail for full text.")) -> incidents
```


## Action Text -> Resolution Details
Evaluate length of action_text:
```{r}
incidents %>% arrange(desc(str_length(incidents$action_text))) %>% head() %>% 
  select(action_text) %>% mutate(str_len_raw = str_length(action_text),
                                 trimmed = str_trim(action_text),
                                 trimed_len = str_length(str_trim(action_text)))

incidents %>% filter(str_length(str_trim(action_text))>1024) %>% tally()
```
```{r message=FALSE, warning=FALSE}
incidents %>% ggplot(aes(str_length(str_trim(action_text)))) + geom_histogram()+geom_vline(xintercept = 1024)
```


```{r}

incidents %>% 
  mutate(out.resolution_details = if_else(is.na(action_text), "", paste0(str_trunc(str_trim(action_text), 986), "\nSee archived detail for full text."))) -> incidents
```

# Build incident types

Mapping to incidents is based off of category and action type initially.

```{r}
incidents %>% mutate(incident_type = case_when(action_type %in% c("Demotion", "Oral", "Suspension", "Termination", "Verbal Warning", "Written") ~ "Disciplinary",
                                               action_type == "Kudos" ~ "Praise",
                                               Category %in% c("Attendance and Punctuality",
                                                               "Continuing Education",
                                                               "Controlled Medication Documentation Error",
                                                               "Customer Service",
                                                               "Distractions and Attentiveness",
                                                               "Failure to complete Station Captain Duties",
                                                               "Incorrect Address Shipped Due to Error",
                                                               "Inventory / Op IQ",
                                                               "Left notes out of an incident-Put units in danger",
                                                               "Lost Equipment",
                                                               "Policy Violation",
                                                               "Self-Reported Violation",
                                                               "Specific Behavior Concern(s)",
                                                               "Station / Unit Inspection",
                                                               "Unprepared for shift",
                                                               "Best Practices Deviation") ~ "Employee Investigation",
                                               Category %in% c("Backing Policy Violation",
                                                               "PPE Deviation",
                                                               "Stage Policy Violation",
                                                               "Vehicle Operations") ~ "Safety Investigation",
                                               Category %in% c("Standard of Care",
                                                               "Protocol Violation / Deviation") ~ "Clinical Performance Investigation",
                                               Violation %in% c("Vehicle Operations Violation", "Safety Violation") ~ "Safety Investigation",
                                               Category %in% c("Kudos customer recognition",
                                                               "Kudos Peer Recognition") ~ "Praise"
                                               ,Violation == "Praise" ~ "Praise"
                                               ,TRUE ~ "Employee Investigation"
                                               )) -> incidents
```



# Import employee info for SSN
```{r}
eeo <- readxl::read_xlsx(here::here("data/VAIRKKO_EEO_Report.xlsx"))
eeo %>% mutate(Member =  paste0(str_replace(`Last Name`, " \\(disabled\\)", ""), ", ", `First Name`)) %>% select(Member, SSN) -> eeo

incidents %>% left_join(eeo) %>% mutate(SSN = if_else(SSN == "Not On File", "", SSN)) -> incidents

incidents %>% filter(SSN == "") %>% arrange(Member) %>%  pull(Member) %>% unique() %>% clipr::write_clip() %>% print()

addl <- readxl::read_xlsx(here::here("data/Additional Employee IDs.xlsx"))

incidents %>%
  left_join(addl %>% select(Member = `Name:`, SSN_x = `SSN:`, `Employee Id` = `Employee ID`)) %>% 
  unite("SSN", SSN, SSN_x, na.rm = TRUE, sep="") -> incidents


```

# Build output
Most of this is straightforward: complete crosswalk joins, bring in existing data, etc.

A few notes: Status is Closed unless there is no Category or no Actions

```{r}
incidents %>% filter(Member != "Person, Test", Violation != "test") %>% # remove tests
  mutate(`EIN Tax Id` = "",
         `EIN Name` = "",
         `Incident Time` = "",
         `Start Date` = "",
         `Reviewer EIN Id` = "",
         `Reviewer EIN Name` = "",
         `Employee External Id` = "",
         `Reviewer Signed Date` = ""
         ) %>% 
  select(Username = out.username,
         `Employee Id`,
         SSN,
         `Employee External Id`,
         `EIN Tax Id`,
         `EIN Name`,
         `Incident Type` = incident_type,
         `Incident Name` = out.incident_name,
         `Internal Name` = out.internal_name,
         `Violation` = out.violation,
         `Incident Date` = out.incident_date,
         `Incident Time`,
         `Report Date` = detail_incident_date,
         `Start Date`,
         `Status` = out.status,
         `Priority` = out.priority,
         `Description` = out.description,
         `Employee Signed Date` = out.signed_date,
         `Reviewer Name` = out.reviewer_name,
         `Reviewer EIN Tax Id` = `Reviewer EIN Id`,
         `Reviewer EIN Name`,
         `Reviewer Signed Date`,
         `Closed Date` = out.closed_date,
         `Target Date` = out.target_date,
         `Resolved Date` = out.closed_date,
         `Resolution` = out.resolution,
         `Details` = out.resolution_details
         ) -> output



source(here::here("R/output_test.R"))
test_output(output) %>% filter(!is.na(test_results)) %>% count(test_results)

# Clean up output

output %>% mutate(across(where(is.character), str_trim)) -> output

output %>% write_excel_csv(here::here("out/export.csv"),
                           na = "")


```
# Download files
How many files?

```{r}
sum(incidents$Files, na.rm=TRUE)
```
Download files
```{r}
download_incident_files(incidents, path=here::here("downloads"))

fs::dir_ls(here::here("downloads")) %>% length()
```
```{r}
download_all_incident_prints(here::here("archives"))
```

